Working title: Ecological network control

### 2018-06-11 paper/manuscript.Rmd
Make figure control capacity
REf #32

```{r, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="unfinished figure"}
drake::loadd(fig_species_level)

fig_species_level[[1]]
```

>>>>

```{r, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="unfinished figure"}
drake::loadd(fig_correlation)
fig_correlation[[1]]
```

```{r, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]*0.5, fig.cap="unfinished figure"}
drake::loadd(fig_control_capacity)
fig_control_capacity[[1]] 
```
